Tampering Detection In Low-Power Smart Cameras

### 2015-05-21 paper.tex
Sistemate immagini

\section{Experiments}\label{sec:experiments}
The proposed algorithm has been implemented in MATLAB, and has been tested on two datasets.
The first one refers to frame sequences taken from webcams recording some parts of cities (as frames illustrated in Figure \ref{fig:buenosAires}), where we have introduced some synthetically generated tampering events:
defocus has been simulated using gaussian filters, while displacement has been created with concatenation of similar frame sequences.
\begin{figure}
	\centering
	\includegraphics[width=1\linewidth]{Immagini/buenosAires}
	\caption{Example of frame sequence taken from webcam. Frames have been acquired every $30$ seconds.}
	\label{fig:buenosAires}
\end{figure}
\begin{figure}
\centering
\subfigure[]{\label{fig:buenosAiresDef} \includegraphics[width=1\linewidth]{Immagini/buenosAiresDef}}
\subfigure[]{\label{fig:buenosAiresDispl} \includegraphics[width=1\linewidth]{Immagini/buenosAiresDispl}}
\caption{Examples of synthetically generated tampering events. \textbf{(a)} Defocus generated with gaussian filters on frames \textit{d} and \textit{e}. \textbf{(b)} Displacement created doing concatenation of similar sequences on frames \textit{d} and \textit{e}.}
\label{fig:buenosAiresTamp}
\end{figure}
In some cases these sequences contained real tampering events, as in Figure \ref{fig:fulvioTestiDispl}.\\
\begin{figure}
\centering
\includegraphics[width=1\linewidth]{Immagini/fulvioTestiDispl}
\caption{Example of sequence taken from webcam in which there is a real displacement (frame \textit{d})}
\label{fig:fulvioTestiDispl}
\end{figure}
The second dataset was taken using a Raspberry Pi Model B+, with its camera module, and the tampering was introduced by moving the device or putting water on the camera.\\
Four figures of merit have been suggested to assess the performance of the proposed algorithm:\\
\begin{description}
	\item[TP]  True positives. It measures the number of tampering events correctly detected by the algorithm.\\ 
	\item[TN]  True negatives. It measures the number of frames without tampering that are not detected by the algorithm. \\ 
	\item[FP]  False positives. It measures the number of tampering events erroneously detected by the algorithm.\\ 
	\item[FN]  False negatives. It measures the number of tampering events not detected by the algorithm. \\ 
\end{description} 
These indicators are computed varying the parameter $\gamma$, which defines the thresholds for the one-shot monitoring. 
This permits us to generate \textit{ROC curves}, where on the x-axis there is:
\[1-\text{SPECIFICITY}_\gamma = 1-\frac{\text{TN}_\gamma}{\text{TN}_\gamma+\text{FP}_\gamma}=\frac{\text{FP}_\gamma}{\text{TN}_\gamma+\text{FP}_\gamma},\]
while on th y-axis there is:
\[\text{RECALL}_\gamma=\frac{\text{TP}_\gamma}{\text{TP}_\gamma+\text{FN}_\gamma}.\]
The construction of these curves permits us to make a comparison with respect to other methods.
In particular the alternative approaches that we have considered working:
\begin{itemize}
\item considering the whole scene for the features computation;
\item considering adaptive region as described in Section \ref{sec:propSol} for the feature computation;
\item considering voronoi regions for the feature computation.
\end{itemize}

\subsection{Alternative Approaches}\label{subsec:AlternativeApproaches}

\subsection{Performance Assessment}
\gi{Adriano: Dire come vengono calcolate le ROC curves TPR e FPR, le cifre di merito insomma, spiegando bene che parametro varia}

\gi{Adriano: metti entrambe le ROC curves, affiancate e per bene ed alcuni esempi di sequenze}

% \begin{figure}
	% \centering
	% \subfigure[]{\label{fig:ROCdisplZOOM} \includegraphics[width=0.45\linewidth]{Immagini/ROCdisplacementZOOM.pdf}}
% %	\subfigure[]{\label{fig:ROCdefocus} \includegraphics[width=0.45\linewidth]{Immagini/ROCdefocus.pdf}}
	% \subfigure[]{\label{fig:ROCdefocusZOOM} \includegraphics[width=0.45\linewidth]{Immagini/ROCdefocusZOOM.pdf}}
% %	\subfigure[]{\label{fig:ROCdispl} \includegraphics[width=0.45\linewidth]{Immagini/ROCdisplacement.pdf}}
	% \caption[Tampering examples]{Examples of tampering events due to atmospheric phenomena. In Figure \ref{fig:neve} there is an occlusion due to some snow on the camera lens, while in Figure \ref{fig:pioggia} there is a blur due to rain drops on the camera lens.}
	% \label{fig:ROC}
% \end{figure}

\begin{figure}
	\centering
	\includegraphics[width=0.7\linewidth]{Immagini/ROCdisplacement_luma}
	\caption[Tampering examples]{Examples of tampering events due to atmospheric phenomena. In Figure \ref{fig:neve} there is an occlusion due to some snow on the camera lens, while in Figure \ref{fig:pioggia} there is a blur due to rain drops on the camera lens.}
	\label{fig:ROCdispl_luma}
\end{figure}

\begin{figure}
	\centering
	\includegraphics[width=0.7\linewidth]{Immagini/ROCdisplacement_fd}
	\caption[Tampering examples]{Examples of tampering events due to atmospheric phenomena. In Figure \ref{fig:neve} there is an occlusion due to some snow on the camera lens, while in Figure \ref{fig:pioggia} there is a blur due to rain drops on the camera lens.}
	\label{fig:ROCdispl_fd}
\end{figure}

\begin{figure}
	\centering
	\includegraphics[width=0.7\linewidth]{Immagini/ROCdefocus1}
	\caption[Tampering examples]{Examples of tampering events due to atmospheric phenomena. In Figure \ref{fig:neve} there is an occlusion due to some snow on the camera lens, while in Figure \ref{fig:pioggia} there is a blur due to rain drops on the camera lens.}
	\label{fig:ROCdispl_luma}
\end{figure}

\begin{figure}
	\centering
	\includegraphics[width=0.7\linewidth]{Immagini/ROCdefocus_fd}
	\caption[Tampering examples]{Examples of tampering events due to atmospheric phenomena. In Figure \ref{fig:neve} there is an occlusion due to some snow on the camera lens, while in Figure \ref{fig:pioggia} there is a blur due to rain drops on the camera lens.}
	\label{fig:ROCdispl_luma}
\end{figure}

%\begin{figure}
%\centering
%\includegraphics[width=0.7\linewidth]{Immagini/ROCdefocus_cropped.pdf}
%\caption{Defocus}
%\label{fig:ROCdefocus}
%\end{figure}

>>>>

\section{Experiments}\label{sec:experiments}
The proposed algorithm has been implemented in MATLAB, and has been tested on two datasets.
The first one refers to frame sequences taken from webcams recording some parts of cities (as frames illustrated in Figure \ref{fig:buenosAires}), where we have introduced some synthetically generated tampering events:
defocus has been simulated using gaussian filters, while displacement has been created with concatenation of similar frame sequences.

In some cases these sequences contained real tampering events, as in Figure \ref{fig:fulvioTestiDispl}.\\
\begin{figure}
\centering
\includegraphics[width=1\linewidth]{Immagini/sequenze}
\caption{Sequences taken from webcams: \textbf{(a)} no tampering events; \textbf{(b)} defocus event on 4-th and 5-th frames, created using gaussian filtering; \textbf{(c)} displacement event on 4-th and 5-th frames, created using concatenation between similar sequences; \textbf{(d)} real displacement event on 4-th frame.}
\label{fig:sequences}
\end{figure}
The second dataset was taken using a Raspberry Pi Model B+, with its camera module, and the tampering was introduced by moving the device or putting water on the camera.\\
Four figures of merit have been suggested to assess the performance of the proposed algorithm:\\
\begin{description}
	\item[TP]  True positives. It measures the number of tampering events correctly detected by the algorithm.\\ 
	\item[TN]  True negatives. It measures the number of frames without tampering that are not detected by the algorithm. \\ 
	\item[FP]  False positives. It measures the number of tampering events erroneously detected by the algorithm.\\ 
	\item[FN]  False negatives. It measures the number of tampering events not detected by the algorithm. \\ 
\end{description} 
These indicators are computed varying the parameter $\gamma$, which defines the thresholds for the one-shot monitoring. 
This permits us to generate \textit{ROC curves}, where on the x-axis there is:
\[1-\text{SPECIFICITY}_\gamma = 1-\frac{\text{TN}_\gamma}{\text{TN}_\gamma+\text{FP}_\gamma}=\frac{\text{FP}_\gamma}{\text{TN}_\gamma+\text{FP}_\gamma},\]
while on th y-axis there is:
\[\text{RECALL}_\gamma=\frac{\text{TP}_\gamma}{\text{TP}_\gamma+\text{FN}_\gamma}.\]
The construction of these curves permits us to make a comparison with respect to other methods.
In particular the alternative approaches that we have considered working:
\begin{itemize}
\item considering the whole scene for the features computation;
\item considering adaptive region as described in Section \ref{sec:propSol} for the feature computation;
\item considering voronoi regions for the feature computation.
\end{itemize}
%
%% \subsection{Alternative Approaches}\label{subsec:AlternativeApproaches}
%
%
%\subsection{Performance Assessment}
%\gi{Adriano: Dire come vengono calcolate le ROC curves TPR e FPR, le cifre di merito insomma, spiegando bene che parametro varia}
%
%\gi{Adriano: metti entrambe le ROC curves, affiancate e per bene ed alcuni esempi di sequenze}
Experimental results are shown in Figures \ref{fig:ROCdispl_luma}, \ref{fig:ROCdispl_fd}, \ref{fig:ROCdef_grad}, \ref{fig:ROCdef_fd}.

\begin{figure}
\centering
\subfigure[]{\label{fig:buenosAiresDef}\includegraphics[width=0.45\linewidth]{Immagini/ROCdisplacement_luma}}
\subfigure[]{\label{fig:buenosAiresDispl} \includegraphics[width=0.45\linewidth]{Immagini/ROCdisplacement_fd}}
\caption{Examples of synthetically generated tampering events. \textbf{(a)} Defocus generated with gaussian filters on frames \textit{d} and \textit{e}. \textbf{(b)} Displacement created doing concatenation of similar sequences on frames \textit{d} and \textit{e}.}
\label{fig:buenosAiresTamp}
\end{figure}

\begin{figure}
\centering
\subfigure[]{\label{fig:buenosAiresDef}\includegraphics[width=0.45\linewidth]{Immagini/ROCdefocus1}}
\subfigure[]{\label{fig:buenosAiresDispl} \includegraphics[width=0.45\linewidth]{Immagini/ROCdefocus_fd}}
\caption{Examples of synthetically generated tampering events. \textbf{(a)} Defocus generated with gaussian filters on frames \textit{d} and \textit{e}. \textbf{(b)} Displacement created doing concatenation of similar sequences on frames \textit{d} and \textit{e}.}
\label{fig:buenosAiresTamp}
\end{figure}
